Perturbation theory in the complex plane: Exceptional points and where to find them

### 2020-11-19 Manuscript/EPAWTFT.tex

The behaviour of the UMP series is more subtle as the spin-contamination comes into play and introduces additional coupling between electronic states.
The UMP partitioning yield the following $\lambda$-dependent Hamiltonian:
\begin{widetext}
\begin{equation}
\label{eq:H_UMP}
	\bH_\text{UMP} = 
	\begin{pmatrix}
		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
	\end{pmatrix},
\end{equation}
\end{widetext}
A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in \titou{Fig.~\ref{eq:UMP_rc}}.

>>>>

The behaviour of the UMP series is more subtle as the spin-contamination comes into play and introduces additional coupling between electronic states.
The UMP partitioning yield the following $\lambda$-dependent Hamiltonian:
\begin{widetext}
\begin{equation}
\label{eq:H_UMP}
	\bH_\text{UMP} = 
	\begin{pmatrix}
		-2t^2 \lambda/U	&	0									&	0									&	+2t^2 \lambda/U		\\
		0				&	U - 2t^2 \lambda/U 					&	+2t^2\lambda/U						&	+2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
		0				&	+2t^2\lambda/U						&	U - 2t^2 \lambda/U 					&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	\\
		+2t^2 \lambda/U	&	+2t \sqrt{U^2 - (2t)^2} \lambda/U 	&	-2t \sqrt{U^2 - (2t)^2} \lambda/U	&	2U(1-\lambda) + 6t^2\lambda/U		\\
	\end{pmatrix},
\end{equation}
\end{widetext}
A closed-form expression for the ground-state energy can be obtained but it is cumbersome, so we eschew reporting it.
The radius of convergence of the UMP series can obtained numerically as a function of $U/t$ and is depicted in Fig.~\ref{fig:RadConv}.
From it, we clearly see that the UMP series has \titou{always?} a larger radius of convergence than the RMP series \titou{(except maybe at $U/t = 2^+$)}, and that the UMP ground-state series is always convergent as $r_c > 1$ for all $U/t$.

\begin{figure}
	\includegraphics[width=\linewidth]{RadConv}
	\caption{
	Evolution of the radius of convergence $r_c$ associated with the RMP ground state (red), the UMP ground state (blue), and the UMP excited state (orange) as functions of the ratio $U/t$.
	\label{fig:RadConv}}
\end{figure}
